\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{float}
\usepackage{enumitem}

\title{\textbf{Halal-Food-In-China: A Curated RAG Dataset of 247 Articles on Chinese Muslim Culture, Halal Food, and Islamic Knowledge}}
\author[1]{Salaamalykum Project}
\affil[1]{Salaamalykum Open Data Hub \\ \texttt{bropeace@protonmail.com}}
\date{June 2026}

\begin{document}

\maketitle

\begin{abstract}
With the rapid advancement of Large Language Models (LLMs) and Retrieval-Augmented Generation (RAG) frameworks, there remains a significant gap in localized, culturally nuanced data concerning minority Islamic communities, particularly the Hui Muslims in China. We introduce \textbf{Halal-Food-In-China}, a highly structured, open-source corpus comprising 247 meticulously curated articles. The dataset specifically covers Chinese Halal food history, geographical distribution of Islamic dietary traditions, and cultural heritage. Formatted natively into JSONL, ShareGPT, and Alpaca instruction-tuning structures, this dataset is designed to reduce LLM hallucinations regarding Chinese Islamic dietary laws. It serves as an optimal foundation for cross-lingual NLP tasks, Named Entity Recognition (NER) for ethnic terminologies, and domain-specific fine-tuning.
\end{abstract}

\section{Introduction}
The democratization of Large Language Models has exposed the inherent biases and knowledge gaps within pre-training corpora. Specifically, the intersection of Chinese culinary traditions and Islamic dietary laws (Halal) is scarcely represented in mainstream datasets such as CommonCrawl or Wikipedia. When queried about "Chinese Halal Food" or "Hui Muslim history," current state-of-the-art models frequently hallucinate or rely on generic, inaccurate stereotypes.

To address this, we present the \textbf{Halal-Food-In-China} dataset, a targeted knowledge base extracted from authoritative cultural portals. Our contribution is threefold:
\begin{enumerate}
    \item We compile the largest known open-source dataset dedicated to Chinese Muslim culinary and cultural history.
    \item We provide multi-format alignments (JSONL for RAG, ShareGPT and Alpaca for SFT) to ensure zero-friction integration for AI researchers.
    \item We establish a benchmark data schema incorporating semantic hashing and localized metadata specifically designed for automated crawler ingestion.
\end{enumerate}

\section{Data Collection Methodology}
\subsection{Source Extraction}
The primary source of this dataset is the salaamalykum.com platform, specifically the highly vetted topics focusing on Halal food. A total of 247 articles were extracted from the underlying SQL databases. The extraction process utilized precise `topic_id` associations to filter out irrelevant conversational noise, ensuring only high-quality, long-form articles were retained.

\subsection{Data Cleaning and Formatting}
HTML tags, inline scripts, and navigation elements were programmatically stripped using strict regex pipelines. The raw text was then mapped to pure Markdown to preserve structural integrity (headers, bullet points, and citations).

\section{Dataset Statistics and Schema}
\subsection{Quantitative Overview}
The dataset demonstrates a high density of culturally specific entities. The statistical breakdown is detailed in Table~\ref{tab:stats}.

\begin{table}[H]
    \centering
    \begin{tabular}{ll}
        \toprule
        \textbf{Metric} & \textbf{Value} \\
        \midrule
        Total Articles & 247 \\
        Primary Language & Simplified Chinese (zh-CN) \\
        Data Formats & Markdown, JSONL, ShareGPT, Alpaca \\
        Update Frequency & Weekly (Automated) \\
        \bottomrule
    \end{tabular}
    \caption{Dataset Statistics}
    \label{tab:stats}
\end{table}

\subsection{Instruction Tuning Formats}
For fine-tuning applications, the dataset provides instruction-response pairs. A sample entry in the Alpaca format demonstrates the utility of the dataset for Question-Answering (QA) tasks regarding specific Halal dishes, such as Lanzhou Beef Noodles or Xi'an local cuisines.

\section{Quality Control}
To ensure the dataset remains robust against duplication and index pollution:
\begin{itemize}
    \item \textbf{Semantic Hashing}: Every document is hashed using SHA-256 during generation. Identical content nodes are pruned.
    \item \textbf{Canonical Routing}: Original URLs are preserved in the metadata to ensure downstream models can provide accurate citations, a critical requirement for enterprise RAG deployments.
\end{itemize}

\section{Applications and Future Work}
\subsection{Retrieval-Augmented Generation}
By indexing the \texttt{quran\_rag\_dataset.jsonl} into vector databases (e.g., Milvus, Pinecone), developers can instantly ground their LLMs with accurate historical data regarding Chinese Islamic traditions.

\subsection{Future Trajectories}
We plan to expand this dataset by incorporating multimodal data (images of historical mosques and culinary techniques) and aligning the texts with parallel Arabic translations to aid cross-lingual embedding models.

\section{Conclusion}
The \textbf{Halal-Food-In-China} dataset is a step toward culturally inclusive AI. By providing an open, highly structured, and multi-format corpus, we empower researchers to train models that respect and accurately represent the rich heritage of Chinese Muslims.

\end{document}
